---
title: "p8105_hw1_at3346"
author: "Ashley Tseng"
date: "9/20/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

# Problem 1

## Creating dataframe and taking means of variables:
```{r problem_1}
set.seed(7)

prob1_df = tibble(
  random_samp = rnorm(8),
  random_samp_zero = random_samp > 0,
  vec_char = c("red", "orange", "yellow", "green", "blue", "purple", "pink", "black"),
  vec_fac = factor(c("high", "medium", "low", "high", "medium", "low", "high", "medium"))
)

mean(prob1_df[["random_samp"]])
mean(prob1_df[["random_samp_zero"]])
mean(prob1_df[["vec_char"]])
mean(prob1_df[["vec_fac"]])

```
I am able to take the mean of "random_samp" and "random_samp_zero", but not of "vec_char" and "vec_fac" because the last two are non-numeric variables.

## Applying the "as.numeric" function to the logical, character, and factor variables:
```{r problem_1_conv, eval = FALSE}
transform(prob1_df, random_samp_zero = as.numeric(random_samp_zero))
transform(prob1_df, vec_char = as.numeric(vec_char)
transform(prob1_df, vec_fac = as.numeric(vec_fac))

```
I am able to convert "random_samp_zero" and "vec_fac", but not "vec_char". The factor variable recognizes that my variable has three different levels, hence why I am able to convert "vec_fac" to a numeric variable. However, R was unable to take the mean of the factor variable when the levels were non-numeric. 

## Converting and multiplying vectors:
```{r problem_1_mult}
mult1 = as.numeric(prob1_df[["random_samp_zero"]])*(prob1_df[["random_samp"]])

mult2 = factor(prob1_df[["random_samp_zero"]])*(prob1_df[["random_samp"]])

conv1 = factor(prob1_df[["random_samp_zero"]])
mult = as.numeric(conv1)*(prob1_df[["random_samp"]])

```


# Problem 2

```{r problem_2}
set.seed(8)

prob2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log = x + y > 1,
  vec_num = as.numeric(vec_log),
  vec_fac = as.factor(vec_log)
)

prob2_df_nrow = nrow(prob2_df)
prob2_df_ncol = ncol(prob2_df)

mean_x = mean(pull(prob2_df, x)) 
median_x = median(pull(prob2_df, x)) 
sd_x = sd(pull(prob2_df, x)) 

vec_gr1 = mean(pull(prob2_df, vec_num))

```
The number of rows in the dataset is `r round(prob2_df_nrow, digits = 0)`. The number of columns in the dataset is `r round(prob2_df_ncol, digits = 0)`. The mean of x is `r round(mean_x, digits = 2)`. The median of x is `r round(median_x, digits = 2)`. The standard deviation of x is `r round(sd_x, digits = 2)`. The proportion of cases for which x + y > 1 is `r round(vec_gr1, digits = 0)`.

## Scatterplots of the logical, numeric, and factor variables:
```{r problem_2_scatterplots}
plot1 = ggplot(prob2_df, aes(x = x, y = y, color = vec_log)) + geom_point()
plot1

plot2 = ggplot(prob2_df, aes(x = x, y = y, color = vec_num)) + geom_point()
plot2

plot3 = ggplot(prob2_df, aes(x = x, y = y, color = vec_fac)) + geom_point()
plot3

ggsave("plot1.pdf")

```

On the scatterplot for the logical variable, points for which "vec_log" = TRUE are displayed in blue while points for which "vec_log" = FALSE are displayed in orange The variable is being displayed as a binary variable.

On the scatterplot for the numeric variable, the legend is a gradient color scale, reflecting a continuous variable. If we look more closely, the points for which "vec_num" = 0 are displayed in dark blue while "vec_num" = 1 are displayed in light blue, indicating that there are only two different values being displayed (0 or 1).

On the scatterplot for the factor variable, points for which "vec_fac" = TRUE are displayed in teal while "vec_fac" = FALSE are displayed in orange The variable is being displayed as a binary variable. The plot for "vec_fac" looks identical to the plot for "vec_log".
