---
title: "p8105_hw1_at3346"
author: "Ashley Tseng"
date: "9/12/2019"
output: github_document
---
library(tidyverse)

prob1_df = tibble(
  random_samp = rnorm(8),
  random_samp_zero = random_samp > 0,
  vec_char = c("red", "orange", "yellow", "green", "blue", "purple", "pink", "black"),
  vec_fac = factor(c("high", "medium", "low", "high", "medium", "low", "high", "medium"))
)

mean(prob1_df[["random_samp"]])
mean(prob1_df[["random_samp_zero"]])
mean(prob1_df[["vec_char"]])
mean(prob1_df[["vec_fac"]])

# I am able to take the mean of "random_samp" and "random_samp_zero", but not of "vec_char" and "vec_fac" because the last two are non-numeric variables.

```{r problem_1_conv}

transform(prob1_df, random_samp_zero = as.numeric(random_samp_zero))
transform(prob1_df, vec_char = as.numeric(vec_char))
transform(prob1_df, vec_fac = as.numeric(vec_fac))

# I am able to convert "random_samp_zero" and "vec_fac", but not "vec_char".

```

```{r problem_1_mult}

mult1 = as.numeric(prob1_df[["random_samp_zero"]])*(prob1_df[["random_samp"]])

mult2 = factor(prob1_df[["random_samp_zero"]])*(prob1_df[["random_samp"]])

conv1 = factor(prob1_df[["random_samp_zero"]])
mult = as.numeric(conv1)*(prob1_df[["random_samp"]])

```

